On Math

### 2025-04-22 cards/paper.tex
more updates
- object displacement calculations
- odd and even functions
- functions compositions
- reciprocal functions

\section{Functions}
\subsection{Quadratic formula}
\begin{equation}
  x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\end{equation}

@@

\subsection{Inverse functions}
Inverse functions are denoted by $f^{-1}(x)$.

@@

\subsection{Exponential functions}
\subsection{Logarithmic functions}
\section{Statistics}
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}

>>>>

\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

$s$ - displacement of the object measured in meters

$u$ - initial velocity of the object measured in meters per second

$t$ - time measured in seconds

$g$ - $9.8\frac{m}{s^2}$ - constant acceleration due to gravity
\section{Functions}
\subsection{Quadratic formula}
\begin{equation}
  x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\end{equation}

\subsection{Odd and even functions}

Function is said to be odd if:
\begin{equation}
  f(-x) = -f(x)
\end{equation}

Function is said to be even if:
\begin{equation}
  f(-x) = f(x)
\end{equation}
\subsection{Factor cubics by grouping}

$3x^3-6x^2+2x-4$

1. group them

$(3x^3-6x^2)+(2x-4)$

2. factor larger terms so the leftover match

$3x^2(x-2)+2(x-2)$

3. factor out the binomial

$(3x^2+2)(x-2)$

Note: not all cubics can be factored, however,
of the cubics that can be factored,
many can be factored by grouping

@@

\subsection{Function composition}
\begin{equation}
  (f \circ g)(x) = f(g(x))
\end{equation}
\subsection{Inverse functions}
Inverse functions are denoted by $f^{-1}(x)$.

@@

\subsection{Reciprocal functions}
\begin{equation}
  f(x) = \frac{1}{x}
\end{equation}
\subsection{Exponential functions}
\subsection{Logarithmic functions}
\section{Statistics}
\subsection{Linear coefficient}
Signed with $\rho$ (Greek letter called 'rho').
- $\rho = 1$ means perfect positive correlation
- $\rho = -1$ means perfect negative correlation
- $\rho = 0$ no (linear) correlation
\section{Logarithms}
\begin{table}[htbp]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Property} & \textbf{Formula} \\
\hline
Product Rule & $\log_a(xy) = \log_a(x) + \log_a(y)$ \\
\hline
Quotient Rule & $\log_a\left(\frac{x}{y}\right) = \log_a(x) - \log_a(y)$ \\
\hline
Power Rule & $\log_a(x^n) = n \cdot \log_a(x)$ \\
\hline
Change of Base & $\log_a(x) = \frac{\log_b(x)}{\log_b(a)}$ \\
\hline
Equating arguments & $\log_af(x) = log_ag(x)$ is the same as $f(x) = g(x)$ \\
\hline
\end{tabular}
\caption{Fundamental Properties of Logarithms}
\label{tab:log_properties}
\end{table}
